\documentclass[11pt,harvard]{article}
\usepackage[letterpaper,top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{graphicx}
\usepackage[sort]{natbib}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{url}
\usepackage{pdflscape}
\usepackage{longtable}
\usepackage{threeparttable, booktabs}
\usepackage[export]{adjustbox}
\usepackage{enumitem}
\usepackage{comment}
\usepackage{subcaption}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{setspace} % Load the setspace package
\usepackage{parskip} % Load the parskip package
\usepackage{float}
\usepackage{subcaption}
\usepackage[table,xcdraw]{xcolor}

\author{Alirah Weyori*  \and   Nicole Wu  \and  Matthieu Tockert  \and  Mohamed Salem}
\date{\today}
\title{Validation and Calibration of the Remote Consolidated Approach of Reporting on Food Security (rCARI) Methodology 
	\\ {\normalsize Preliminary results from Myanmar, Ecuador, and Central African Republic} 
	\\{\normalsize{Version 1.0}} | \emph{{\normalsize{To add comments, open the PDF document in MS Word directly}} }}

\begin{document}
	\maketitle \vspace{-1cm}
	\onehalfspacing
	\pagebreak
	\setlength{\parskip}{8pt} % Set the desired space before and after paragraphs
	
	% ------- 
	\section{Introduction}
	The overall goal of this study was to assess the validity of the rCARI module(s) against conventional CARI modules for measuring food security within the same population. The study will compare the indicators measured through phone surveys with conventional face-to-face survey indicators, considering the latter as the so-called “gold standard.” The following food security indicators were compared (FCS, LCS, rCSI, FES, income sources, and income change). The ECMEN indicator will not be tested in this study, as it requires a standard expenditure module, which cannot be collected over the phone. A shortened version of the standard expenditure module will be used to test the possibility of collecting FES data over the phone.
	
	Studying the validity of the phone modality in collecting food security indicators is a key step in judging the appropriateness of using the rCARI module to estimate food security prevalence. If needed, the validation will be followed by calibration to ensure that the modality of data collection has minimal influence on the estimate (rCARI).
	
	However, several other factors should be considered while reading estimates of any indicator (whether it is food security or not) when it comes from a nationally representative phone survey.
	
	\begin{itemize}[label=--, left=1.5em]
		\item Mobile phone ownership (mobile phone penetration rate) excluded the most vulnerable population from the sample. In some countries where WFP operates, the penetration rate is as low as 30%, whereas in others, it exceeds 100%.
		\item Mobile phone network coverage: Even in countries with high penetration rates, network coverage could be a problem, especially when electricity cuts are frequent and local infrastructure, such as communication masts, are not evenly distributed (World Bank, 2020).
		\item Response rate: It is well documented that the response rate in phone surveys is usually lower than in face-to-face surveys (L’Engle et al., 2018; World Bank, 2020).
	\end{itemize}
	
	These factors usually lead to a skewed sample; nevertheless, there are several weighting techniques to adjust the results of phone surveys based on the demographics of the most recent face-to-face surveys (Nagpal et al. 2021; Glazerman et al. 2020; Valliant et al. 2013; Elkasabi, 2015).
	
	This study does not cover weighting techniques to adjust for the sampling frame and response rate issued to produce a national estimate. This has been covered in the literature, and several studies have been conducted to control for these biases.
	
	\pagebreak
	
	% ------- 
	\section{Study design}
	
	The study was implemented in a randomized controlled setup. 
	Food security data were collected from two statistically comparable groups of households within the same sample. Stand-alone standardized remote and face-to-face questionnaires will be administered to sampled households randomized to receive either modalities-remote or face-to-face. The study will be implemented across six countries: two in Africa, two Latin America, one in Southeast Asia, and one in the Middle East. 
	
	\subsection{Selection of study areas and participants}
	
	The selection of study villages proceeded as described in (figure 1).Listing of potential households/respondents to form the sampling frame after taking their informed consent (a minimum of 100 households per village/lowest admin area/camp, i.e., 2000hh in total will be listed through a random walk approach). For purposes of statistical comparison, demographic information will collected from all households contacted during the listing phase. Households that agreed to be listed for the study are randomly assigned into one of two modalities (groups) in a pure random assignment; 1000 households receiving the remote/phone interview (called the treatment group) and 1000 households assigned to receive the face-to-face interview (called the control group). 
	The study will aim to achieve a minimum of 600 completed interviews for each modality from the originally assigned groups (i.e., there will be no replacement for non responses).  
	
	\subsection{Implementation}
	
	Fieldwork was originally planned to take place over a 3 week period (covering 1 week for enumerator training, adjusting questionnaire and 2 weeks for actual household interviews) in each pilot country. However, because of unforeseen challenges as will be discussed later, data collection was extended by between 2 to 3 weeks depending on the country.
	
	\pagebreak
	
	% ------- 
	\section{Sample Completion}
	Table 1 Shows the total sample and households interviews completed by country and modality in the initial 3 pilot countries of the study. Generally, the figures in Table 1 show that we have lower response rate across countries for the remote modality.
	
	\input{1_table/rCARI_Overall_Completion} 
	\label{tab:rCARI_Overall_Completion}
	
	\pagebreak
	
	% ------- 
	\section{Primary Results: Impact of Survey Modality}
	
	In this section, we present the main results of the study aggregated by the food security indicator. Here, the main objective is to compare the different CARI variations aggregated either using remote or face-to-face modules.
	CARI aggregated using remote modules is referred to us rCARI (remote CARI). Depending on the indicators used, we have CARI-FES and CARI-Inc which is CARI aggregated using the standard FES (food expenditure share) and income and income change variables respectivey. 
	For the purposes of this interim analysis and report, we restrict the CAR sample to only respondents that owned phones (the complete sample comprising respondents that received phones is available upon request).  
	
	\subsection{CARI vs. rCARI}
	There are four versions of overall indicators we used in the validation study:
	\begin{itemize}[label=--, left=1.5em]
		\item CARI-FES: Standard CARI using FES module from F2F surveys
		\item rCARI-FES: CARI using FES module from Remote surveys
		\item CARI-Inc: CARI using Income & income change from F2F surveys
		\item rCARI-Inc: Standard rCARI using Income & income change module from Remote surveys
	\end{itemize}
	
	From Table 2, we have three different CARI aggregation methods to test against the standard/gold-standard CARI. We will further compare the results of rCARI aggregated using FES with rCARI using the income and income change variables.
	
	\begin{table}[htbp]
		\centering
		\begin{adjustbox}{max width=\textwidth}
			\begin{threeparttable}
				\caption{Lists the different aggregation methods and indicators used for each methodology}
				\scriptsize
				\input{1_table/Aggregation_Table} 
				\label{tab:Aggregation_Table}
			\end{threeparttable}
		\end{adjustbox}
	\end{table}
	
	\begin{table}[htbp]
		\centering
		\begin{adjustbox}{max width=\textwidth}
			\begin{threeparttable}
				\caption{Impact of Survey Modality: Standard CARI-FES vs. Standard rCARI-Inc}
				\scriptsize
				\input{1_table/CARI_rCARI_Modality_All_Country} 
				\label{tab:CARI_rCARI_Modality_All_Country}
				\begin{tablenotes}[para,flushleft]
					\item Note: Significance: * p$<$0.05, ** p$<$0.01, *** p$<$0.001. 
				\end{tablenotes}
			\end{threeparttable}
		\end{adjustbox}
	\end{table}
	
	Table 3 presents the first comparison of rCARI (using the income & income change variable) with the standard CARI across the 3 pilot countries. The results from this table show two key findings. First, except for CAR, the calculated food insecurity category (moderately food insecure plus severely food insecure categories) did not differ significantly between the two methods. Second, although the results were not statistically different between the two aggregation methods, rCARI is always the conservative method (reporting lower food insecure numbers) relative to stanadard CARI.
	
	\begin{table}[htbp]
		\centering
		\begin{adjustbox}{max width=\textwidth}
			\begin{threeparttable}
				\caption{Impact of Survey Modality: CARI-FES vs. rCARI-FES}
				\scriptsize
				\input{1_table/CARI_FES_rCARI_Modality_All_Country} 
				\label{tab:CARI_FES_rCARI_Modality_All_Country}
				\begin{tablenotes}[para,flushleft]
					\item Note: Significance: * p$<$0.05, ** p$<$0.01, *** p$<$0.001. 
				\end{tablenotes}
			\end{threeparttable}
		\end{adjustbox}
	\end{table}
	
	Table 4 shows the results of rCARI aggregated using the FES module collected over the phone, which is a relatively shorter version of the standard FES usually collected in F2F surveys. This version collects the household's aggregate expenditure without going through individual items. 
	The results show that rCARI using FES consistently over-states the number of food insecure across all countries compared to the standard CARI by between 2 and 17 percentage points. This difference was statistically significant in Myanmar and Ecuador.
	
	\begin{table}[htbp]
		\centering
		\begin{adjustbox}{max width=\textwidth}
			\begin{threeparttable}
				\caption{Impact of Survey Modality: CARI-Inc vs. rCARI-Inc}
				\scriptsize
				\input{1_table/Inc_CARI_rCARI_Modality_All_Country} 
				\label{tab:Inc_CARI_rCARI_Modality_All_Country}
				\begin{tablenotes}[para,flushleft]
					\item Note: Significance: * p$<$0.05, ** p$<$0.01, *** p$<$0.001. 
				\end{tablenotes}
			\end{threeparttable}
		\end{adjustbox}
	\end{table}
	
	A comparison of results using income and income change modules implemented over the phone (rCARI) and in F2F interviews is presented in Table 5. Aside from CAR, the results show that the module when implemented over the phone produces a significantly higher number of food insecurities compared to when asked in an F2F. This difference was between 9 and 10 percent points. 
	
	Next, we investigate how CARI aggregated using FES with income and income change variables modules collected in F2F surveys from the same households/respondents. This step allowed the comparison of these two indicators using the same respondents in the same modality. Results for the 3 pilot countries are presented in Table 6. The main conclusion is that CARI aggregated using income and income change variable significantly understates the numbers of food insecure (6 percent in Myanmar, 23 percent in Ecuador and 22 percent in CAR).
	
	\begin{table}[htbp]
		\centering
		\begin{adjustbox}{max width=\textwidth}
			\begin{threeparttable}
				\caption{Impact of Indicator Composition: Paired CARI-FES vs. CARI-Inc in F2F Surveys}
				\scriptsize
				\input{1_table/Paired_F2F_CARI_FES_INC_All_Country} 
				\label{tab:Paired_F2F_CARI_FES_INC_All_Country}
				\begin{tablenotes}[para,flushleft]
					\item Note: Significance: * p$<$0.05, ** p$<$0.01, *** p$<$0.001. \\
					For CAR, the sample is limited to phone owners only.
				\end{tablenotes}
			\end{threeparttable}
		\end{adjustbox}
	\end{table}
	
	Similar to the comparison between the FES and income variables in the F2F modality, we investigate the performance of these variables (FES and the income and income change variables) in the remote modality. Reported in Table 7, we find that the income and income change variable is conservatively under reporting the number of food insecure by between 12 to 24 percentage points (12 percent in Myanmar, 19 percent in Ecuador and 24 percent in CAR). 
	
	\begin{table}[htbp]
		\centering
		\begin{adjustbox}{max width=\textwidth}
			\begin{threeparttable}
				\caption{Impact of Indicator Composition: Paired rCARI-FES vs. rCARI-Inc in Remote Surveys}
				\scriptsize
				\input{1_table/Paired_RM_rCARI_FES_INC_All_Country} 
				\label{tab:Paired_RM_rCARI_FES_INC_All_Country}
				\begin{tablenotes}[para,flushleft]
					\item Note: Significance: * p$<$0.05, ** p$<$0.01, *** p$<$0.001. \\
					For CAR, the sample is limited to phone owners only.
				\end{tablenotes}
			\end{threeparttable}
		\end{adjustbox}
	\end{table}
	
	\clearpage
	
	\subsection{FCS}
	
	The results of the FCS show that respondents tend to overestimate their consumption (report better food consumption) over the phone compared to when interviewed in F2F. This is statistically significant in Ecuador and Myanmar. The result for Myanmar remains the same across both modalities (F2F and remote) showing no significant difference. This is reflected in the 3-phase food consumption classification, more households in the F2F category significantly are classified as having poor food consumption compared to those in the remote category (see Table 6 for details). 
	
	\begin{table}[htbp]
		\centering
		\begin{adjustbox}{max width=\textwidth}
			\begin{threeparttable}
				\caption{Impact of Survey Modality on Food Consumption Score and Groups}
				\scriptsize
				\input{1_table/FCS_Modality_All_Country} 
				\label{tab:FCS_Modality_All_Country}
				\begin{tablenotes}[para,flushleft]
					\item Note: Significance: * p$<$0.05, ** p$<$0.01, *** p$<$0.001. 
				\end{tablenotes}
			\end{threeparttable}
		\end{adjustbox}
	\end{table}
	
	\pagebreak
	
	\subsection{rCSI}
	
	The rCSI results in Table 7 show that in Myanmar and CAR, households tend to report that they are adopting more reduced coping strategies over the phone compared to F2F. However, the opposite is found for Ecuador where F2F respondents are adopting significantly higher reduced coping strategies.
	
	\begin{table}[htbp]
		\centering
		\begin{adjustbox}{max width=\textwidth}
			\begin{threeparttable}
				\caption{Impact of Survey Modality on Reduced Coping Strategy Index and IPC Phases}
				\scriptsize
				\input{1_table/rCSI_Modality_All_Country} 
				\label{tab:rCSI_Modality_All_Country}
				\begin{tablenotes}[para,flushleft]
					\item Note: Significance: * p$<$0.05, ** p$<$0.01, *** p$<$0.001. 
				\end{tablenotes}
			\end{threeparttable}
		\end{adjustbox}
	\end{table}
	
	\pagebreak
	
	\subsection{LCS}
	
	The livelihood coping strategy adoption by respondents for none and stress level across countries follows the same trend (higher adoption in F2F than remote), however the results are mixed comparing the crisis and emergency levels. For example, while the result shows a significantly higher adoption of these categories by households taking the remote interviews in Myanmar and CAR, the opposite is observed for crisis level in Ecuador. Worthy of mention is the fact that in Ecuador, there is big jump in the adoption of emergency category strategies between F2F and remote (50\% more households in the remote interview indicated adopted a strategy from this broad category). 
	
	\begin{table}[htbp]
		\centering
		\begin{adjustbox}{max width=\textwidth}
			\begin{threeparttable}
				\caption{Impact of Survey Modality on Livelihood Coping Strategy Index}
				\scriptsize
				\input{1_table/LCS_Modality_All_Country} 
				\label{tab:LCS_Modality_All_Country}
				\begin{tablenotes}[para,flushleft]
					\item Note: Significance: * p$<$0.05, ** p$<$0.01, *** p$<$0.001. 
				\end{tablenotes}
			\end{threeparttable}
		\end{adjustbox}
	\end{table}
	
	\begin{table}[htbp]
		\centering
		\begin{adjustbox}{max width=\textwidth}
			\begin{threeparttable}
				\caption{Myanmar: Each Coping Strategy Used}
				\scriptsize
				\input{1_table/LCS_Ind_Modality_Myanmar} 
				\label{tab:LCS_Ind_Modality_Myanmar}
				\begin{tablenotes}[para,flushleft]
					\item Note: Significance: * p$<$0.05, ** p$<$0.01, *** p$<$0.001. 
				\end{tablenotes}
			\end{threeparttable}
		\end{adjustbox}
	\end{table}
	
	\begin{table}[htbp]
		\centering
		\begin{adjustbox}{max width=\textwidth}
			\begin{threeparttable}
				\caption{Ecaudor: Each Coping Strategy Used}
				\scriptsize
				\input{1_table/LCS_Ind_Modality_Ecuador} 
				\label{tab:LCS_Ind_Modality_Ecuador}
				\begin{tablenotes}[para,flushleft]
					\item Note: Significance: * p$<$0.05, ** p$<$0.01, *** p$<$0.001. 
				\end{tablenotes}
			\end{threeparttable}
		\end{adjustbox}
		
	\end{table}
	\begin{table}[htbp]
		\centering
		\begin{adjustbox}{max width=\textwidth}
			\begin{threeparttable}
				\caption{CAR: Each Coping Strategy Used}
				\scriptsize
				\input{1_table/LCS_Ind_Modality_CAR} 
				\label{tab:LCS_Ind_Modality_CAR}
				\begin{tablenotes}[para,flushleft]
					\item Note: Significance: * p$<$0.05, ** p$<$0.01, *** p$<$0.001. 
				\end{tablenotes}
			\end{threeparttable}
		\end{adjustbox}
	\end{table}
	
	\pagebreak
	
	\subsection{FES}
	
	The aggregated FES show that across the 3 pilot countries, respondents over the phone tend to state their FES share on average by between 5\% and 8\% compared to F2F. This is significantly reflected in the 75\% and above category.
	
	\begin{table}[htbp]
		\centering
		\begin{adjustbox}{max width=\textwidth}
			\begin{threeparttable}
				\caption{Impact of Survey Modality on Expenditure and Food Expenditure Share}
				\scriptsize
				\input{1_table/FES_Modality_All_Country} 
				\label{tab:FES_Modality_All_Country}
				\begin{tablenotes}[para,flushleft]
					\item Note: Significance: * p$<$0.05, ** p$<$0.01, *** p$<$0.001. \\ 
					In Myanmar, the Short Form in Remote Survey was dropped due to translation issues.
				\end{tablenotes}
			\end{threeparttable}
		\end{adjustbox}
	\end{table}
	
	\pagebreak
	
	\subsection{Income}
	
	The income source and income change variable, behaves differently across modality in the 3 pilot countries. For example, fewer households reported no income source on the phone compared to those interviewed in the F2F modality. This result remains consistent in all 3 pilot countries. The results of the comparison of the two versions of the rCARI is presented in Table 7.   
	
	\begin{table}[htbp]
		\centering
		\begin{adjustbox}{max width=\textwidth}
			\begin{threeparttable}
				\caption{Impact of Survey Modality on Income}
				\scriptsize
				\input{1_table/INC_Modality_All_Country} 
				\label{tab:INC_Modality_All_Country}
				\begin{tablenotes}[para,flushleft]
					\item Note: Significance: * p$<$0.05, ** p$<$0.01, *** p$<$0.001. 
				\end{tablenotes}
			\end{threeparttable}
		\end{adjustbox}
	\end{table}
	
	In the next section, we will investigate the individual indicators used in calculating the CARI console. We would look at how these indicators compare across modalities (F2F and Remote).
	
	\pagebreak
	
	% ------- 
	\section{Impact of Form Length on FCS and Expenditure/FES}
	
	As a secondary objective, the study also tested a modified version of FCS and FES modules. We test an aggregated (shorter versions) with the standard version (long version) of these indicators. Since, speedily collection of data particularly in emergency situation is relevant for timely analysis and interventions, validating the shorter modules could help improve the data collection time. This is particularly important for remote data collection where duration of the interview is inversely related to quality of responses (the longer the interview, the lower the quality of the data). 
	Results from these comparison will feed into the recommendation on collecting FES data over the phone or F2F surveys in general to reduce interviewee fatigue and curb erroneous reporting. Finally, we will also test the LCS-EN module against LCS-FS module to identify their convergence or otherwise. 
	
	\subsection{FCS Full Subgroup vs. FCS Short}
	
	In terms of FCS (see Table 16), the results are not significantly different between short and long modules in Myanmar and Ecuador except for CAR where the short version significantly overstates food consumption by 4.35 points.
	
	\begin{table}[htbp]
		\centering
		\begin{adjustbox}{max width=\textwidth}
			\begin{threeparttable}
				\caption{Impact of Module Length on FCS Reporting}
				\scriptsize
				\input{1_table/FCS_F2F_Form_Length_All_Country} 
				\label{tab:FCS_F2F_Form_Length_All_Country}
				\begin{tablenotes}[para,flushleft]
					\item Note: Significance: * p$<$0.05, ** p$<$0.01, *** p$<$0.001. 
				\end{tablenotes}
			\end{threeparttable}
		\end{adjustbox}
	\end{table}
	
	\subsection{Expenditure Long vs. Short}
	
	The FES however remains stable showing no statistical significance between the short and long modules in all pilot countries (see Tables 17). The results are similar for the two versions used in the remote surveys (showing no significant difference between short and long).
	
	\begin{table}[htbp]
		\centering
		\begin{adjustbox}{max width=\textwidth}
			\begin{threeparttable}
				\caption{Impact of Module Length on Expenditure and FES in F2F Surveys}
				\scriptsize
				\input{1_table/FES_F2F_Form_Length_All_Country} 
				\label{tab:FES_F2F_Form_Length_All_Country}
				\begin{tablenotes}[para,flushleft]
					\item Note: Significance: * p$<$0.05, ** p$<$0.01, *** p$<$0.001. 
				\end{tablenotes}
			\end{threeparttable}
		\end{adjustbox}
	\end{table}
	
	\begin{table}[htbp]
		\centering
		\begin{adjustbox}{max width=\textwidth}
			\begin{threeparttable}
				\caption{Impact of Module Length on Expenditure and FES in Remote Surveys}
				\scriptsize
				\input{1_table/FES_RM_Form_Length_ECU_CAR} 
				\label{tab:FES_RM_Form_Length_ECU_CAR}
				\begin{tablenotes}[para,flushleft]
					\item Note: Significance: * p$<$0.05, ** p$<$0.01, *** p$<$0.001. \\
					Myanmar is excluded due to translation issue.
				\end{tablenotes}
			\end{threeparttable}
		\end{adjustbox}
	\end{table}
	
	\begin{table}[htbp]
		\centering
		\begin{adjustbox}{max width=\textwidth}
			\begin{threeparttable}
				\caption{Impact of Module Length on Expenditure and FES: F2F vs. Remote Long}
				\scriptsize
				\input{1_table/FES_F2F_Long_All_Country} 
				\label{tab:FES_F2F_Long_All_Country}
				\begin{tablenotes}[para,flushleft]
					\item Note: Significance: * p$<$0.05, ** p$<$0.01, *** p$<$0.001. 
				\end{tablenotes}
			\end{threeparttable}
		\end{adjustbox}
	\end{table}
	
	\begin{table}[htbp]
		\centering
		\begin{adjustbox}{max width=\textwidth}
			\begin{threeparttable}
				\caption{Impact of Module Length on Expenditure and FES: F2F vs. Remote Short}
				\scriptsize
				\input{1_table/FES_F2F_Short_ECU_CAR} 
				\label{tab:FES_F2F_Short_ECU_CAR}
				\begin{tablenotes}[para,flushleft]
					\item Note: Significance: * p$<$0.05, ** p$<$0.01, *** p$<$0.001. \\
					Myanmar is excluded due to translation issue.
				\end{tablenotes}
			\end{threeparttable}
		\end{adjustbox}
	\end{table}
	
	\pagebreak
	
	% ------- 
	\section{Impact of LCS for Essential Needs or Food Security}
	
	\subsection{Overall}
	\begin{table}[htbp]
		\centering
		\begin{adjustbox}{max width=\textwidth}
			\begin{threeparttable}
				\caption{Myanmar: LCS for Essential Needs vs. Food Security}
				\scriptsize
				\input{1_table/LCS_F2F_EN_FS_All_Country} 
				\label{tab:LCS_F2F_EN_FS_All_Country}
				\begin{tablenotes}[para,flushleft]
					\item Note: Significance: * p$<$0.05, ** p$<$0.01, *** p$<$0.001. 
				\end{tablenotes}
			\end{threeparttable}
		\end{adjustbox}
	\end{table}
	\pagebreak
	
	\subsection{Specific Strategy}
	\begin{table}[htbp]
		\centering
		\begin{adjustbox}{max width=\textwidth}
			\begin{threeparttable}
				\caption{Myanmar: LCS for Essential Needs vs. Food Security}
				\scriptsize
				\input{1_table/LCS_F2F_EN_FS_Myanmar} 
				\label{tab:LCS_F2F_EN_FS_Myanmar}
				\begin{tablenotes}[para,flushleft]
					\item Note: Significance: * p$<$0.05, ** p$<$0.01, *** p$<$0.001. 
				\end{tablenotes}
			\end{threeparttable}
		\end{adjustbox}
	\end{table}
	
	\begin{table}[htbp]
		\centering
		\begin{adjustbox}{max width=\textwidth}
			\begin{threeparttable}
				\caption{Ecuador: LCS for Essential Needs vs. Food Security}
				\scriptsize
				\input{1_table/LCS_F2F_EN_FS_Ecuador} 
				\label{tab:LCS_F2F_EN_FS_Ecuador}
				\begin{tablenotes}[para,flushleft]
					\item Note: Significance: * p$<$0.05, ** p$<$0.01, *** p$<$0.001. 
				\end{tablenotes}
			\end{threeparttable}
		\end{adjustbox}
	\end{table}
	
	\begin{table}[htbp]
		\centering
		\begin{adjustbox}{max width=\textwidth}
			\begin{threeparttable}
				\caption{CAR: LCS for Essential Needs vs. Food Security}
				\scriptsize
				\input{1_table/LCS_F2F_EN_FS_CAR} 
				\label{tab:LCS_F2F_EN_FS_CAR}
				\begin{tablenotes}[para,flushleft]
					\item Note: Significance: * p$<$0.05, ** p$<$0.01, *** p$<$0.001. 
				\end{tablenotes}
			\end{threeparttable}
		\end{adjustbox}
	\end{table}
	
	
\end{document}
